\LARGE \bf{Hall C 12 GeV Trigger Set-Up}

### 2022-01-18 MY_THESIS_DOCS/D2_Optics_Optim/d2_optim.tex
re-structure

offsets based on observations in H(e,e'p) elastic run 3288, as it is closest in kinematic to the Deuteron 80 MeV setting.

@@

The central angle offsets can be determined from the missing momentum components for H(e,e'p) elastics, as these should ideally be centered around
zero. In Hall Coordinate System (HCS), the in-plane central angle offset can be determined by taking the fractional dfference between

>>>>

offsets based on observations in H(e,e'p) elastic run 3288, as it is closest in kinematic to the deuteron 80 MeV setting.

@@

The central angle offsets can be determined from the missing momentum components for H(e,e'p) elastics, as these should ideally
be centered around zero. In Hall Coordinate System (HCS), the in-plane central angle offset can be determined by taking the fractional dfference between

### 2022-01-18 MY_THESIS_DOCS/DETECTORS/Hodoscope_Calib_Doc/hodo_calib.tex
re-structure

\maketitle
\noindent The Hall C Scintillaror Hodoscopes consists on four planes (per spectrometer) of scintillator arrays oriented perpendicular
to the beam direction(See Figure \ref{fig:Hodo}). Each spectrometer has two sets of planes, each set oriented along the +X and +Y in the hut coordinate system.
The hodoscopes form the standard HMS/SHMS trigger in Hall C due to the fast signal rise time produced from the scintillating material.
For a thorough discussion of how the trigger is formed, see . . . \\
\begin{figure}[H]
  \captionsetup{justification=raggedright,singlelinecheck=false}
  \includegraphics[scale=0.3]{Hodo.png}
  \caption{HMS Hodoscope 1X and 1Y Planes.}
  \label{fig:Hodo}
\end{figure}
When a particle traverses a plane, depending on the trajectory, any paddle could in principle be hit,
the paddle then scintillates light, which propagates to them photomultiplier tubes (PMTs) at the two ends. The PMTs
convert the incident light to photoelectrons in the photocathode. The photoelectrons then are guided through the various dynodes in the PMT, knocking
out more electrons, creating an avalanche of electrons. The electron avalanche then reaches the anode, producing a measurable current signal.
The signal is sent to the Counting Room, where it is processed by the NIM/CAMAC electronics, and ultimately sent to ADCs, and TDCs. At this stage, the raw tdc signal
has multiple unwanted timing contributions which must be subtracted to obtain the true arrival time at the hodoscope plane. The corrected tdc time is the used to determine
the correct particle velocity, $\beta = \frac{v}{c}$. The determination and correction for the additional timing from the raw tdc is the essence of the hodoscope timing
calibration, and will be discussed next.

@@

  same time. Analog-to-Digital Converters (ADCs), do not have this disadvantage, since they correct for time-walk internally,
  and as a result, the ADC Pulse Time is not correlated with the signal amplitude. To correct for this correlation in the TDCs,
  the ADC Pulse Time is used as a reference by taking the TDC-ADC Pulse Time difference is plotted against the ADC amplitude. A model
  function is fitted to this correlation, and the parameters extracted are used to correct the TDC time.

@@

The plot in Figure \ref{fig:TWFit} shows the correlation between TDC Pulse Time and ADC Pulse Amplitude.  The fit parameters, $c_{1}$, TDC Threshold are read in by hcana, where
the time-walk correction is applied to the raw TDC to obtain the corrected tdc time as shown in Figure \ref{fig:TWCorr}.

@@

The cable time offset parameter is determined for all paddles and the parameter is read by hcana, and added as a correction

@@

\item Propagation Time Corrections, $t_{prop.}$: This correction accounts for the propagation
  time across both ends of the scintillator paddle from the particle hit location. The corrections is
  done in the Hall C Analyzer, \textit{hcana}. Some of the geometrical parameters that are used are shown
  in Figure \ref{fig:propTime}. \\
  \begin{figure}[H]
    \captionsetup{justification=raggedright,singlelinecheck=false}
    \includegraphics[scale=0.48]{propTime_Corr.png}
    \caption{Scintillator paddle illustrating how to apply the propagation time corrections.}
    \label{fig:propTime}
  \end{figure}
  To derive how this correction is done in hcana, let the time-walk and cable length corrected time be
  defined as
  \begin{equation}
    t^{\pm}_{Corr.} = t_{0} + t^{\pm}_{prop.}
  \end{equation}
  The path length from the center of the paddle to the hit can then be defined as
    \begin{align}
      \Delta L &= \frac{1}{2}(t^{(-)}_{Corr.} - t^{(+)}_{Corr.})v_{p} =  \frac{1}{2}(t^{(-)}_{prop.} - t^{(+)}_{prop.})v_{p}
    \end{align}
    The equations used in hcana are
    \begin{align}\label{eq:11}
      t^{(+)}_{Corr.} = t^{(+)}_{Corr.} - (L_{+} - hit)\frac{1}{v_{p}}, \text{ where } t^{(+)}_{prop.}\equiv(L_{+} - hit)\frac{1}{v_{p}} \nonumber \\
      t^{(-)}_{Corr.} = t^{(-)}_{Corr.} - (hit - L_{-})\frac{1}{v_{p}}, \text{ where } t^{(-)}_{prop.}\equiv(hit - L_{-})\frac{1}{v_{p}}       
    \end{align}
    Substituting the definitions from Figure \ref{fig:propTime}  into Eq.\ref{eq:11}, after some algebra, one is able to prove that
    \begin{equation}
      t_{avgCorr} = \frac{1}{2}( t^{(+)}_{Corr.} +  t^{(-)}_{Corr.}) = \frac{1}{2} (t^{(+)}_{TWC_{orr.}} +  t^{(-)}_{TW_{Corr.}})
    \end{equation}
    where the propagation time has been corrected for.
\end{itemize}

@@

\section{Hodoscope Calibration Procedure}
In this section I will discuss the procedure to perform the hodoscopes calibration
using the new method.
\begin{itemize}
\item Set the flag \texttt{h(p)tofusinginvadc = 0} to NOT use the hodo parameters from the
  previous hodoscope calibration procedure. This flag is found on \texttt{hallc\_replay/PARAM/H(S)MS/HODO/} directory.
\item Replay the raw data file, typically 1-2 M events is required for a good fit to be done.   
\item In the directory \texttt{hallc\_replay/CALIBRATION/(s)hms\_hodo\_calib/}, run the following code:
  \subitem $\Diamond$ {\texttt{root -l ''timeWalkHistos.C(<run\_num>)''} \\
  This script takes as input the ROOTfile replayed and creates another ROOTfile with histogram
  objects that are used to perform the time-walk correction.}
\item To do the time-walk corrections, run the following code:
  \subitem $\Diamond$ {\texttt{root -l ''timeWalkCalib.C(<run\_num>)''}} \\
  This script takes as input the ROOTfile containing the histogram objects produced by the previous
  script.  A parameter file containing the time-walk parameters will be produced at 
  \subitem $\Diamond$ {\texttt{hallc\_replay/PARAM/(S)HMS/HODO/(p)hhodo\_TWcalib\_runNUM.param}}
  This parameter file name has to be manually changed to exclude the run number, since hcana reads in the parameter file as
  \texttt{(p)hhodo\_TWcalib.param} .
\item Replay the raw data file, once again (1 - 2 M events), with the updated time-walk parameters.
\item In the hodoscopoe calibration directory, run the following code:
  \subitem $\Diamond$ {\texttt{root -l fitHodoCalib.C}}
  The first part of this script performs a linear fit on the time-walk corrected time vs. hodoscope track
  to determine the propagation velocity and the cable time difference across each paddle. The second part of
  this code solves a matrix equation for the $\lambda$ parameters mentioned in the previous section.
  A parameter file containing the time-walk parameters will be produced at
  \subitem $\Diamond$ {\texttt{hallc\_replay/PARAM/(S)HMS/HODO/(p)hhodo\_Vpcalib\_runNUM.param}} \\
  This parameter file name has to be manually changed to exclude the run number, since hcana reads in the parameter file as
  \texttt{(p)hhodo\_Vpcalib.param} .
\item {Replay the raw data one last time, and check the hodoscope beta distribution. You may have to apply a calorimeter cut (for example, \texttt{(P)H.cal.etracknorm>0.7})}
  A good calibration should have the beta centered at unity. (See Figure \ref{fig:beta})
\end{itemize}
\begin{figure}[H]
    \captionsetup{justification=raggedright,singlelinecheck=false}
    \includegraphics[scale=0.7]{hms_betaCompare.pdf}
    \caption{Comparison between HMS $\beta$ distributions using the original and new calibration procedure.}
    \label{fig:beta}
\end{figure}
%HHODO_vPcalib.param, fitHodoCalib.C

>>>>

\maketitle
\noindent The Hall C Scintillaror Hodoscopes consists of four planes (per spectrometer) of scintillator arrays oriented perpendicular
to the beam direction(See Figure \ref{fig:Hodo}). Each spectrometer has two sets of planes, each set oriented along the +X and +Y in the hut coordinate system.
The hodoscopes form the standard HMS/SHMS trigger in Hall C due to the fast signal rise time produced from the scintillating material.
For a thorough discussion of how the trigger is formed, see \url{https://hallcweb.jlab.org/doc-private/ShowDocument?docid=1028}  \\
\begin{figure}[H]
  \captionsetup{justification=raggedright,singlelinecheck=false}
  \includegraphics[scale=0.3]{Hodo.png}
  \caption{HMS Hodoscope 1X and 1Y Planes.}
  \label{fig:Hodo}
\end{figure}
When a particle traverses a plane, depending on the trajectory, any paddle could in principle be hit,
the paddle then scintillates light, which propagates to the photomultiplier tubes (PMTs) at the two ends. The PMTs
convert the incident light to photoelectrons in the photocathode. The photoelectrons then are guided through the various dynodes in the PMT, knocking
out more electrons, creating an avalanche of electrons. The electron avalanche then reaches the anode, producing a measurable current signal.
The signal is sent to the Counting Room, where it is processed by the NIM/CAMAC electronics, and ultimately sent to ADCs, and TDCs. At this stage, the raw tdc signal
has multiple unwanted timing contributions which must be subtracted to obtain the true arrival time at the hodoscope plane. The corrected tdc time is the used to determine
the correct particle velocity, $\beta = \frac{v}{c}$. The determination and correction for the additional timing from the raw tdc is the essence of the hodoscope timing
calibration, and will be discussed next.

@@

  same time. Flash Analog-to-Digital Converters (fADCs), do not have this disadvantage, since they correct for time-walk internally,
  and as a result, the ADC Pulse Time is not correlated with the signal amplitude. To correct for this correlation in the high resolution TDCs,
  the ADC Pulse Time is used as a reference by taking the TDC-ADC Pulse Time difference is plotted against the fADC amplitude. A model
  function is fitted to this correlation, and the parameters extracted are used to correct the TDC time. (See Figure \ref{fig:TWFit}) The function that is currently
  being used in Hall C analyzer, \texttt{hcana}, has the form:
    f_{TW}(a) = \frac{1}{(\frac{a}{TDC_{Thrs.}})^{c_{2}}} - \frac{1}{(\frac{200}{TDC_{Thrs.}})^{c_{2}}}
  where $a$ is the ADC amplitude,  $TDC_{Thrs}$ is the TDC threshold which is currently set to 120 mV. \textbf{ONLY} the fit parameter, $c_{2}$, and the
  TDC Threshold ($TDC_{Thrs.}$), are read in by \texttt{hcana}, where the time-walk correction is applied to the raw TDC to obtain the corrected tdc time as shown in Figure \ref{fig:TWCorr}.
  Even though the baseline parameter, $c_{1}$, is extracted in the calibration code, it is actually \textbf{NOT} used in \texttt{hcana} as it is highly correlated with the parameter $c_{2}$.
  As a solution, an empirical baseline:  $-\frac{1}{(\frac{200}{TDC_{Thrs.}})^{c_{2}}}$, is used in \texttt{hcana} to replace $c_{1}$.

@@

The plot in Figure \ref{fig:TWFit} shows the correlation between TDC Pulse Time and ADC Pulse Amplitude.

@@

The cable time offset parameter is determined for all paddles and the parameter is read by \texttt{hcana}, and added as a correction

@@

\item Propagation Time Corrections, $t_{prop.}$: This correction accounts for the propagation
  time across both ends of the scintillator paddle from the particle hit location. The corrections is
  done in the Hall C Analyzer, \texttt{hcana}. Some of the geometrical parameters that are used are shown
  in Figure \ref{fig:propTime}. \\
  \begin{figure}[H]
    \captionsetup{justification=raggedright,singlelinecheck=false}
    \includegraphics[scale=0.48]{propTime_Corr.png}
    \caption{Scintillator paddle illustrating how to apply the propagation time corrections.}
    \label{fig:propTime}
  \end{figure}
  To derive how this correction is done in \texttt{hcana}, let the time-walk and cable length corrected time be
  defined as
  \begin{equation}
    t^{\pm}_{Corr.} = t_{0} + t^{\pm}_{prop.}
  \end{equation}
  The path length from the center of the paddle to the hit can then be defined as
    \begin{align}
      \Delta L &= \frac{1}{2}(t^{(-)}_{Corr.} - t^{(+)}_{Corr.})v_{p} =  \frac{1}{2}(t^{(-)}_{prop.} - t^{(+)}_{prop.})v_{p}
    \end{align}
    The equations used in \texttt{hcana} are
    \begin{align}\label{eq:11}
      t^{(+)}_{Corr.} = t^{(+)}_{Corr.} - (L_{+} - hit)\frac{1}{v_{p}}, \text{ where } t^{(+)}_{prop.}\equiv(L_{+} - hit)\frac{1}{v_{p}} \nonumber \\
      t^{(-)}_{Corr.} = t^{(-)}_{Corr.} - (hit - L_{-})\frac{1}{v_{p}}, \text{ where } t^{(-)}_{prop.}\equiv(hit - L_{-})\frac{1}{v_{p}}       
    \end{align}
    Substituting the definitions from Figure \ref{fig:propTime}  into Eq.\ref{eq:11}, after some algebra, one is able to prove that
    \begin{equation}
      t_{avgCorr} = \frac{1}{2}( t^{(+)}_{Corr.} +  t^{(-)}_{Corr.}) = \frac{1}{2} (t^{(+)}_{TWC_{orr.}} +  t^{(-)}_{TW_{Corr.}})
    \end{equation}
    where the propagation time has been corrected for.
\end{itemize}

@@

\section{Hodoscope Calibration Procedure}
In this section I will discuss the procedure to perform the hodoscopes calibration
using the new method.
\begin{itemize}
\item Set the flag \texttt{h(p)tofusinginvadc = 0} to NOT use the hodo parameters from the
  previous hodoscope calibration procedure. This flag is found on \texttt{hallc\_replay/PARAM/H(S)MS/HODO/} directory.
\item Replay the raw data file, typically 1-2 M events is required for a good fit to be done.   
\item In the directory \texttt{hallc\_replay/CALIBRATION/(s)hms\_hodo\_calib/}, run the following code:
  \subitem $\Diamond$ {\texttt{root -l ''timeWalkHistos.C(<run\_num>)''} \\
  This script takes as input the ROOTfile replayed and creates another ROOTfile with histogram
  objects that are used to perform the time-walk correction.}
\item To do the time-walk corrections, run the following code:
  \subitem $\Diamond$ {\texttt{root -l ''timeWalkCalib.C(<run\_num>)''}} \\
  This script takes as input the ROOTfile containing the histogram objects produced by the previous
  script.  A parameter file containing the time-walk parameters will be produced at 
  \subitem $\Diamond$ {\texttt{hallc\_replay/PARAM/(S)HMS/HODO/(p)hhodo\_TWcalib\_runNUM.param}}
  This parameter file name has to be manually changed to exclude the run number, since \texttt{hcana} reads in the parameter file as
  \texttt{(p)hhodo\_TWcalib.param} .
\item Replay the raw data file, once again (1 - 2 M events), with the updated time-walk parameters.
\item In the hodoscopoe calibration directory, run the following code:
  \subitem $\Diamond$ {\texttt{root -l fitHodoCalib.C}}
  The first part of this script performs a linear fit on the time-walk corrected time vs. hodoscope track
  to determine the propagation velocity and the cable time difference across each paddle. The second part of
  this code solves a matrix equation for the $\lambda$ parameters mentioned in the previous section.
  A parameter file containing the time-walk parameters will be produced at
  \subitem $\Diamond$ {\texttt{hallc\_replay/PARAM/(S)HMS/HODO/(p)hhodo\_Vpcalib\_runNUM.param}} \\
  This parameter file name has to be manually changed to exclude the run number, since \texttt{hcana} reads in the parameter file as
  \texttt{(p)hhodo\_Vpcalib.param} .
\item {Replay the raw data one last time, and check the hodoscope beta distribution. You may have to apply a calorimeter cut (for example, \texttt{(P)H.cal.etracknorm>0.7})}
  A good calibration should have the beta centered at unity. (See Figure \ref{fig:beta})
\end{itemize}
\begin{figure}[H]
    \captionsetup{justification=raggedright,singlelinecheck=false}
    \includegraphics[scale=0.7]{hms_betaCompare.pdf}
    \caption{Comparison between HMS $\beta$ distributions using the original and new calibration procedure.}
    \label{fig:beta}
\end{figure}
%HHODO_vPcalib.param, fitHodoCalib.C

### 2022-01-18 MY_THESIS_DOCS/HallC_12GeV_Trigger/version2/trigger_v2.tex
re-structure

\begin{figure}[h!]
  \includegraphics[scale=0.5]{../CR_patch_combined.png}
  \caption{(A) Counting Room Patch Panels (left 2 racks). (B) Counting Room main
    Electronic Racks for HMS/SHMS detectors (right 2 racks).}
  \label{fig:cr_racks_patch}
\end{figure}
\newpage
\section{HMS Trigger Set-Up} 
\indent The XY scintillator arrays (hodoscope planes) will form part of the standard HMS trigger configuration.  
Additional particle detectors may also be incorporated into the HMS trigger as required by different experiments. The Gas \v{C}erenkov and Calorimeter triggers will be
used for e/$\pi$ separation, whereas the Aerogel \v{C}erenkov trigger will be used for $\pi$/K/p separation.

\subsection{Hodoscope Pre-Trigger}
\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.5]{hHODO_diagram.png}
  \caption{HMS Hodoscope Electronics Diagram. For original diagram, see Appendix \ref{appendix:AppxA1}}
  \label{fig:hHODO_diagram}
\end{figure}
\noindent Each hodoscope plane consists of an array of scintillator bars coupled to a PMT at each end (See Figure \ref{fig:hms_stack}), so each bar reads out two signals. As shown in Figure \ref{fig:hHODO_diagram},
for example, hodoscope plane h1X consists of 32 signals (16 bars) read out in the Counting House (CH) patch. Each side of the plane (x16 signals/side) is fed into a 64-channel input passive splitter (16 Ch./set).
One-third (33\%) of the signal amplitude is sent via a 16-channel ribbon cable to a 64 Ch. input Ribbon-to-BNC converter (16 Ch./set) which outputs are fed into a 16-channel NIM input flash ADC (fADC). The remaining two-thirds (66\%)
of the signal amplitude is sent to a 16-Ch. input CAMAC Discriminator unit. The HMS discriminators thresholds and gate widths were set to \hhodthrs and \hhodgate, respectively.\\
\indent The discriminated signals are sent via two ribbon-cable outputs to CAEN1190 TDCs/Scalers (daisy-chained) and to a LeCroy 4564 CAMAC Logic unit to form the plane pre-triggers.
The Logic Unit takes four sets of 16-Ch. input ribbon cable and forms a 16-fold OR for each set by default. Further boolean operations are done through the module backplane by connecting a twisted pair cable to the pin corresponding to the
desired boolean operation. For hodoscope plane pre-triggers, the boolean operations are as follows:
\begin{empheq}[box=\fbox]{align*}
& \text{h1X = h1X+ (16-fold OR) \textit{AND} h1X- (16-fold OR)} \\ 
& \text{h1Y = h1Y+ (10-fold OR) \textit{AND} h1Y- (10-fold OR)} \\
& \text{h2X = h2X+ (16-fold OR) \textit{AND} h2X- (16-fold OR)} \\ 
& \text{h2Y = h2Y+ (10-fold OR) \textit{AND} h2Y- (10-fold OR)} 
\end{empheq}

@@

\subsection{Calorimeter Pre-Trigger}
\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.5]{hCAL_diagram.png}
  \caption{HMS Calorimeter Electronics Diagram. For original diagram, see Appendix \ref{appendix:AppxA2}}
  \label{fig:hCAL_diagram}
\end{figure}
\noindent The HMS Calorimeter consists of four layers of lead blocks. Layers A and B read out a 26 PMT signals per layer (13 signals/side) while layers C and D
read out 13 signals/layer on one side. The first two layers form the Pre-Shower Counter while all four layers (A, B, C and D) form the Shower Counter.  
Each layer is read out in the Counting Room patch and fed into 50:50 splitters. One output of the splitter is fed to fADCs via a Ribbon-to-BNC converter (same as hodoscopes)
while the other output is sent to a P/S Model 740 NIM Linear FI/FO summing modules. Each side of a layer is summed first (hA+, hA-, hB+, hB-, hC and hD sums). The sums are fed into
a LeCroy Model 428F summing module where layers hA+/- and hB+/- are summed to form hA and hB sums. A copy of each layer sum is sent to fADCs. The Pre-Shower SUM is then made from the sum of layers A and B, while the Shower SUM is made by summing all four layers. A copy of the PreShower and Shower sums is also sent to fADCs. The Pre-Shower and Shower sums are then sent to a P/S Model 715
NIM Discriminator unit to form the PreShower Low/High (LO/HI) and Shower Low pre-triggers with thresholds \hPrShLo, \hPrShHi and \hSHLo, respectively with all gate widths set to 30 ns. A copy of the pre-triggers is sent to TDCs/Scaler modules for trigger timing and counting rate
information.

>>>>

\begin{figure}[h!]
  \includegraphics[scale=0.5]{../CR_patch_combined.png}
  \caption{(A) Counting Room Patch Panels (left 2 racks). (B) Counting Room main
    Electronic Racks for HMS/SHMS detectors (right 2 racks).}
  \label{fig:cr_racks_patch}
\end{figure}

\newpage
\section{HMS Trigger Set-Up} 
\indent The XY scintillator arrays (hodoscope planes) will form part of the standard HMS trigger configuration.  
Additional particle detectors may also be incorporated into the HMS trigger as required by different experiments. The Gas \v{C}erenkov and Calorimeter triggers will be
used for $e/\pi$ separation, whereas the Aerogel \v{C}erenkov trigger will be used for $\pi/K/p$ separation.

\subsection{Hodoscope Pre-Trigger}
\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.5]{../hHODO_diagram.png}
  \caption{HMS Hodoscope Electronics Diagram. For original diagram, see Appendix \ref{appendix:AppxA1}}
  \label{fig:hHODO_diagram}
\end{figure}
\noindent Each hodoscope plane consists of an array of scintillator bars coupled to a PMT at each end (See Figure \ref{fig:hms_stack}), so each bar reads out two signals. As shown in Figure \ref{fig:hHODO_diagram},
for example, hodoscope plane h1X consists of 32 signals (16 bars) read out in the Counting House (CH) patch. Each side of the plane (x16 signals/side) is fed into a 64-channel input passive splitter (16 Ch./set).
One-third (33\%) of the signal amplitude is sent via a 16-channel ribbon cable to a 64 Ch. input Ribbon-to-BNC converter (16 Ch./set) which outputs are fed into a 16-channel NIM input flash ADC (fADC). The remaining two-thirds (66\%)
of the signal amplitude is sent to a 16-Ch. input CAMAC Discriminator unit. The HMS discriminators thresholds and gate widths were set to \hhodthrs and \hhodgate, respectively.\\
\indent The discriminated signals are sent via two ribbon-cable outputs to CAEN1190 TDCs/Scalers (daisy-chained) and to a LeCroy 4564 CAMAC Logic unit to form the plane pre-triggers.
The Logic Unit takes four sets of 16-Ch. input ribbon cable and forms a 16-fold OR for each set by default. Further boolean operations are done through the module backplane by connecting a twisted pair cable to the pin corresponding to the
desired boolean operation. For hodoscope plane pre-triggers, the boolean operations are as follows:
\begin{empheq}[box=\fbox]{align*}
& \text{h1X = h1X+ (16-fold OR) \textit{AND} h1X- (16-fold OR)} \\ 
& \text{h1Y = h1Y+ (10-fold OR) \textit{AND} h1Y- (10-fold OR)} \\
& \text{h2X = h2X+ (16-fold OR) \textit{AND} h2X- (16-fold OR)} \\ 
& \text{h2Y = h2Y+ (10-fold OR) \textit{AND} h2Y- (10-fold OR)} 
\end{empheq}

@@

\subsection{Calorimeter Pre-Trigger}
\begin{figure}[h!]
  \centering
  \includegraphics[scale=0.5]{hCAL_diagram.png}
  \caption{HMS Calorimeter Electronics Diagram. For original diagram, see Appendix \ref{appendix:AppxA2}}
  \label{fig:hCAL_diagram}
\end{figure}
\noindent The HMS Calorimeter consists of four layers of lead blocks. Layers A and B read out a 26 PMT signals per layer (13 signals/side) while layers C and D
read out 13 signals/layer on one side. The first layer form the Pre-Shower counter while all four layers (A, B, C and D) form the Shower counter.  
Each layer is read out in the Counting Room patch and fed into 50:50 splitters. One output of the splitter is fed to fADCs via a Ribbon-to-BNC converter (same as hodoscopes)
while the other output is sent to a P/S Model 740 NIM Linear FI/FO summing modules. Each side of a layer is summed first (hA+, hA-, hB+, hB-, hC and hD sums). The sums are fed into
a LeCroy Model 428F summing module where layers hA+/- and hB+/- are summed to form hA and hB sums. A copy of each layer sum is sent to fADCs. The Pre-Shower SUM is then made from the sum of layer A, while the Shower SUM is made by summing all four layers. A copy of the Pre-Shower and Shower sums is also sent to fADCs. The Pre-Shower and Shower sums are then sent to a P/S Model 715
NIM Discriminator unit to form the PreShower Low/High (LO/HI) and Shower Low pre-triggers with thresholds \hPrShLo, \hPrShHi and \hSHLo, respectively with all gate widths set to 30 ns. A copy of the pre-triggers is sent to TDCs/Scaler modules for trigger timing and counting rate
information.
